### 2015-11-02 CVPR16/Source/experiments.tex
Generated visualizations.

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Algorithm & Total & Unoccluded cars & Occluded cars \\
    \midrule
    bounding box only & 0.21 & \textbf{0.03}  & 0.36\\
    Using $P^{(ij)}_{\text{assoc}}$ & \textbf{0.21} & 0.08 & \textbf{0.32}\\
    Using $\assocP{}$ & 0.23 & 0.09 & 0.34 \\
    Using $P^{(ij)}_{\text{assoc by reproj}}$ & 0.23 & 0.08 & 0.34\\
    \bottomrule
  \end{tabular}
  \caption{Association Experiment results. The error is in terms of fraction of points wrongly associated with objects, hence lower is better.}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Energy & t & yaw & dim \\
    \midrule
    lane+contPtTracksNoOcc+size+bbox+posT   & 3.80 & 0.91 & 1.58 \\
    lane+contPtTracks+size+bboxOcc+posT+col & \textbf{3.78} & 0.91 & 1.58 \\
    lane+contPtTracks+size+bboxOcc+posT     & 3.81 & 0.92 & 1.59 \\
    lane+size+bboxOcc+posT+col              & 3.92 & 0.91 & 1.15 \\
    lane+size+bboxOcc+posT                  & 3.83 & 0.90 & 1.14 \\
    lane+size+bbox+posT                     & 3.83 & 0.90 & \textbf{1.14} \\
    initialization                          & 3.79 & \textbf{0.86} & 1.64 \\
    \bottomrule
  \end{tabular}
  \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
\end{table}

>>>>

% \begin{table}
%   \centering
%   \begin{tabular}{lrrr}
%     \toprule
%     Algorithm & Total & Unoccluded cars & Occluded cars \\
%     \midrule
%     bounding box only & 0.21 & \textbf{0.03}  & 0.36\\
%     Using $P^{(ij)}_{\text{assoc}}$ & \textbf{0.21} & 0.08 & \textbf{0.32}\\
%     Using $\assocP{}$ & 0.23 & 0.09 & 0.34 \\
%     Using $P^{(ij)}_{\text{assoc by reproj}}$ & 0.23 & 0.08 & 0.34\\
%     \bottomrule
%   \end{tabular}
%   \caption{Association Experiment results. The error is in terms of fraction of points wrongly associated with objects, hence lower is better.}
% \end{table}

%\begin{table}
%  \centering
%  \begin{tabular}{lccc}
%    \toprule
%    Algorithm & All & Unoccluded cars & Occluded cars \\
%    \midrule
%    bounding box only                         & $0.18\pm0.01$          & $\color{red}0.04\pm0.003$  & $0.41\pm0.04$\\
%    Using $\assocP{}$                         & $0.18\pm0.01$          & $0.05\pm0.003$           & $0.39\pm0.04$ \\
%    Using $P^{(ij)}_{\text{assoc by reproj}}$ & $0.18\pm0.01$          & $0.06\pm0.003$           & $0.39\pm0.04$\\
%    Using $P^{(ij)}_{\text{assoc}}$           & $\color{red}0.17\pm0.01$ & $0.05\pm0.003$           & $\color{red}0.38\pm0.04$\\
%    \bottomrule
%  \end{tabular}
%  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
%\end{table}
\begin{figure*}
  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_occ_50.pdf}
  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
  \label{fig:assoc-occ-results}
\end{figure*}

@@

% \begin{table}
%   \centering
%   \begin{tabular}{lrrr}
%     \toprule
%     Energy & t & yaw & dim \\
%     \midrule
%     initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
%     $\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
%     %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
%     %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
%     %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
%     $\EnergyLane+\EnergyTrackNoOcc+\EnergySize+\EnergyBBox+\EnergyDyn+\EnergyCol $ & 3.80 & 0.91 & 1.58 \\
%     $\EnergyLane+\EnergyTrack+\EnergySize+\EnergyBBox+\EnergyDyn+\EnergyCol   $ & \textbf{3.78} & 0.91 & 1.58 \\
%     \bottomrule
%   \end{tabular}
%   \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
% \end{table}

\newpage
\begin{table*}
  \begin{tabular}{ccc}
    & Assignments & Error in assignment\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{05pt} Brox and Malik} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{05pt} Brox and Malik} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
\end{table*}

### 2015-11-02 CVPR16/Source/occlusion.tex
Generated visualizations.

In practice, the integral for transmission probability \eqref{eq:ptrans-integral} is difficult to compute even numerically. So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability:
%
\begin{align}
  P^j_{\textit{transmission}}(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \nu_i)),
\label{eq:evalCumulativePtrans}
\end{align}
%
where $\cL_u(.)$ is sigmoid in image domain, with $\bmu^i_u$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain with $\nu_i$ the mean depth of object $O_i$. That is,
%
\begin{align}
\cL_u(\bu; \bmu_i, \bGamma_i^{-1}) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}} \\
\cL_{\lambda}(\lambda; \nu_i) &= \frac{1}{1 + e^{-k_d(\lambda - \nu_i)}}
\end{align}
%

>>>>

In practice, the integral for transmission probability \eqref{eq:ptrans-integral} is difficult to compute even numerically. So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability:
%
%\newcommand{\Ptrans}{P_{\textit{transmission}}}%
\begin{align}
  \Ptrans^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \nu_i)),
\label{eq:evalCumulativePtrans}
\end{align}
%
where $\cL_u(.)$ is sigmoid in image domain, with $\bmu^i_u$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain with $\nu_i$ the mean depth of object $O_i$. That is,
%
\begin{align}
\cL_u(\bu; \bmu_i, \bGamma_i^{-1}) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}} \\
\cL_{\lambda}(\lambda; \nu_i) &= \frac{1}{1 + e^{-k_d(\lambda - \nu_i)}}
\end{align}
%
We compare the exact and relative formulation of transmission probability in Fig~\ref{fig:compare:exact:approx:ptrans}.

\begin{figure}
  \includegraphics[width=\columnwidth]{results/plotPtransmission_exact_vs_approx.pdf}
  \caption{Comparing the approximate $\Ptrans$ with exact version. The drop in approximate version of $\Ptrans$ is delayed because we assume drop at the center of the car rather than camera facing face of the car.}
  \label{fig:compare:exact:approx:ptrans}
\end{figure}
